Modeling How Evolution in One Trait is Affected by Adaptation in Another

### 2017-07-17 manuscript.tex
more updates

Evolutionary theory for the in our understanding of trait correlations and their role in evolution surfaced as the conAdvances in our understanding of trait correlatiosn and their role in evolution have been limited, Plant and animal breeders preceding Darwin trait associations in domesticated stocks influence their response to artificial selection, and early breeders preceding Darwin often had to account for this in their selection programs (cite).  Darwin’s own considerations of this fact naturally led him to posit an important role for them in adaptive evolution (Darwin p. 144-150).  However, the lack of quantitative descriptions hindered the exploration of have been two major approaches to address questions in this area with the common aim of elucidating further on the complex dynamics of adaptation with multiple traits. One of the earliest theoretical treatments of adaptation in a multivariate trait space was put forth by R.A. Fisher in The Genetical Theory of Natural Selection (1930). The model provides a simple geometric argument demonstrating how adaptive evolution would be constrained in higher dimensional trait spaces.  Kimura (1983) gave further extensions to this model by incorporating probability of fixation, and Orr (1998, 2000) provided additional insights on the the optimal dimensions that ensured maximum adaptation.  Some of the earliest works that attempted to address multi-trait adaptation were developed by Fisher (1930)However, early evolutionary biology could provide little development in this area, in part due to standing questions concerning the relationships between traits and their genetic foundation, such as how to reconcile Mendelian genetics and with the inheritance of continuous characters. Thus questions concerning whole organisms, which are of main interest to plant and animal breeders, and the level of whole organisms.\par

@@

\section*{Appendix A:}
\section*{Appendix B:}
\section*{Appendix C:}
\end{document}

>>>>

Darwin himself realized that trait correlations could significantly influence adaptive evolution (Darwin p. 144-150).  However, the first theoretical insights  but it would take many more years and the insights of the modern synthesis before evolutionary biologists could begin addressing questions in this area.  The lack of quantitative descriptions hindered the exploration of have been two major approaches to address questions in this area with the common aim of elucidating further on the complex dynamics of adaptation with multiple traits. One of the earliest theoretical treatments of adaptation in a multivariate trait space was put forth by R.A. Fisher in The Genetical Theory of Natural Selection (1930). The model provides a simple geometric argument demonstrating how adaptive evolution would be constrained in higher dimensional trait spaces.  Kimura (1983) gave further extensions to this model by incorporating probability of fixation, and Orr (1998, 2000) provided additional insights on the the optimal dimensions that ensured maximum adaptation.  Some of the earliest works that attempted to address multi-trait adaptation were developed by Fisher (1930)However, early evolutionary biology could provide little development in this area, in part due to standing questions concerning the relationships between traits and their genetic foundation, such as how to reconcile Mendelian genetics and with the inheritance of continuous characters. Thus questions concerning whole organisms, which are of main interest to plant and animal breeders, and the level of whole organisms.\par

@@

\section*{Appendix A:}

\end{document}
